Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-07 1_introduction/introduction.tex
no message

Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}. Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs. Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out. In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}. This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.

>>>>

Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}. Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs. Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out. In the cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison are \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}. This study is based on the environment where processes are executed in several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.

### 2015-11-07 3_background/background.tex
no message

In this section, process discovery methods and mismatch patterns are presented within the scope of this work. In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations. In this study, since the focus is learning lessons from cross-organizational mining, we used Inductive Process Mining \cite{leemans2013discovering} for process discovery, which is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

>>>>

In this section, process discovery methods and mismatch patterns are presented within the scope of this work. In the process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations. In this study, since the focus is learning lessons from cross-organizational mining, we used Inductive Process Mining \cite{leemans2013discovering} for process discovery, which is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

### 2015-11-07 4_methodology/methodology.tex
no message

\subsection{Approach Overview}
\label{subsec:approach-overview}
The approach proposed in this study consists of four main stages visualized in Figure~\ref{fig:approach-overview}. Firstly, in \textit{Process Model Mining}, process models are extracted from event logs for each organization with a user specified noise threshold. Secondly, in \textit{Performance Indicator Analysis}, event logs are replayed on process models and performance indicators are calculated for each organization then using these indicators, organizations are clustered based on how well they are operating. Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns. Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/approach-overview}
  \caption{Overview of Methodology}
  \label{fig:approach-overview}
\end{figure}

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

\subsection{Genarating Suggestions/Recommendations for Performance Improvement}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.

>>>>

\subsection{Approach Overview}
\label{subsec:approach-overview}
The approach proposed in this study consists of four main stages visualized in Figure~\ref{fig:approach-overview}. Firstly, in \textit{Process Model Mining}, process models are extracted from event logs for each organization with a user specified noise threshold. Secondly, in \textit{Performance Indicator Analysis}, event logs are replayed on process models and performance indicators are calculated for each organization then using these indicators, organizations are clustered based on how well they are operating. Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns. Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models; a set of recommendations for each organization is generated.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/approach-overview}
  \caption{Overview of Methodology}
  \label{fig:approach-overview}
\end{figure}

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

\subsection{Genarating Suggestions/Recommendations for Performance Improvement}
\label{subsec:recommendation-generation}
Recommendation generation stage in the methodology is the final and core stage where all information retrieved from the event logs until now are utilized. In this study, idea of recommendation is based on providing a set of mismatch patterns for each organization so that they can enhance their processes. These mismatch patterns are generated by comparing the process models of other organizations, particularly those that are performing better in terms of their performance indicator values. In addition, clustering of organizations is undertaken to generalize the way of identifying which organizations perform better in this environment.

### 2015-11-07 paper.tex
no message

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved within evaluation metrics. Generated recommendation results indicate that the use of this approach can help users to focus on the parts of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}

>>>>

\begin{abstract}
Process mining is a relatively young and developing research area with the main idea of discovering, monitoring and improving processes by extracting information from event logs. With the increase of cloud computing and shared infrastructures, event logs of multiple organizations are available for analysis where cross-organizational process mining stands with the opportunity for organizations learning from each other. The approach proposed in this study mines process models of organizations and calculates performance indicators; followed by clustering of organizations based on performance indicators and finally spots mismatches between the process models to generate recommendations. This approach is implemented as an extensible and configurable plug-in set in ProM framework and tested by synthetic and real life logs where successful and suitable results are achieved with defined evaluation metrics. Generated recommendation results indicate that the use of this approach can help users to focus on the parts of process models with potential performance improvement, which are difficult to spot manually and visually.
\end{abstract}
